---
title: "Walkthrough"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Walkthrough}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

This document gives you a walkthrough of the package and describes 
several usecases. I assume you have knowledge of downloading and installing
a package.

```{r glossary}
library(dplyr)# for this specific part
tibble::tribble(
        ~Term, ~explanation,
        "API", "Application Programming Interface, a term most often used when describing an internet endpoint (but also used within a single piece of software to describe what parts can be used by other programs). An internet API allows us to send a request to a service and recieve a standardized result back.",
        "OMDBapi", "Open Movie Database API",
        ".Rrnviron", "When R starts it reads in this file and adds all keys to it's configuration. This allows you to access keys without ever putting them in your console."
)
```

## First use - get a key
To use the service, you need a key. This key identifies you for OMDBapi.
Go to the website omdbapi.com and click on get key or go directly
to <http://omdbapi.com/apikey.aspx>

If you want to support the OMDBapi authors on Patreon use that option otherwise
use the free option, and input your email adres.

I think you recieve an email with the key in it.

## First use - save the key safely
*You don't have to add this key to a file, you can call every function with the key argument filled. However this makes it difficult to share a script (it has you secret key in that file!).*

We want R to have access to the key and not retype the key with every request.
That is why we save the key to a file that is read by R on startup.
This file is called .Renviron (the dot means it's normally hidden from view)
Either go manually to ~/.Renviron (On windows )

```{r, eval=FALSE}
file.edit("~/.Renviron")
```

More info on: <https://csgillespie.github.io/efficientR/3-3-r-startup.html#renviron> and <https://stat.ethz.ch/R-manual/R-devel/library/base/html/Startup.html> 

Or use the convenience function I added to this package:

```{r eval=FALSE}
library(imdb)
add_key_to_renviron("fillInYourKeyHere")
```

If you leave the key empty a prompt will ask you for the key (that way it never gets recorded in your .Rhistory file).

## I want to download imdb information for a movie (I know the title)

Use the title to search for a movie.

This returns a dataframe with a row for every match. 
```{r}
library(imdb)
movies <- imdbMovies(moviename = "2001 a space odyssey")
movies[,c(1:7,15:18)]
```



## I want to download basic information about a series (I know the title)

This downloads a dataframe with all episodes.

```{r}
library(imdb)
series <- imdbSeries("The Orville")
series
```


## I want to download more information about a series

Use the enrichIMDB function to add more information to
the series you downloaded.

```{r}
series <- enrichIMDB(df = series)
series[1:2,]
```


## I know the imdbID and want to download that specific information

If you have imdbID's and want more information about a that title 
you can use the imdbTitleId function to download that specific 
information from the API.

For instance I want to know more about 'The Truman Show', it has id 'tt0120382'.

```{r}
trumanshow <- imdbTitleId("tt0120382")
trumanshow
```

# I want something else

I'm sorry, I don't have more. You can always ask a question by opening 
an [issue](https://github.com/RMHogervorst/imdb/issues) on github. 


